Races with hyper3 objects

### 2022-04-17 inst/race3.Rmd
constructor's championship 2021

constructor_table_2021 <- jj[,-ncol(jj)]
constructor_table_2021[,1:10]
```

@@

```{r,maketheconst,cache=TRUE}
constructor_2021 <- ordertable2supp3(constructor_table_2021)
pnames(constructor_2021) <- names(constructor_points_2021)
```

@@

```{r,label=saveconstructordataset}
save(constructor_2021_maxp,constructor_2021,constructor_table_2021,file="constructor.rda")
```

>>>>

constructor_table_2021 <- jj[,-ncol(jj)]
constructor_table_2021[,1:10]
constructor_2021_table <- constructor_table_2021
```

@@

```{r,maketheconst,cache=TRUE}
constructor_2021 <- ordertable2supp3(constructor_table_2021)
```

@@

```{r,label=saveconstructordataset}
save(
constructor_2021_maxp,
constructor_2021,
constructor_2021_table,
file="constructor.rda")
```
